Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-10 paper/paper.tex
concl

\section{Conclusions}
\label{sec:conclusion}
%% We  have  defined  a  notion  of liveness  on  structured  data;  this
%% generalizes classical liveness and strong liveness.  We started with a
%% general fully context-sensitive analysis  which we proved correct with
%% respect to  a minefield semantics  (this models the effect  of garbage
%% collection between every evaluation step).

@@

\subsection{Future work}
Although we  provide an  implementation for  a liveness  based garbage
collection scheme for lazy language, we  do not provide a formal proof
of its correctness.  A formal  proof of correctness would describe how
closures  are  handled  during  garbage  collection  and  liveness  is
propogated inside closures.

>>>>

\section{Conclusions and Future Work}
\label{sec:conclusion}
%% We  have  defined  a  notion  of liveness  on  structured  data;  this
%% generalizes classical liveness and strong liveness.  We started with a
%% general fully context-sensitive analysis  which we proved correct with
%% respect to  a minefield semantics  (this models the effect  of garbage
%% collection between every evaluation step).

@@

%%\subsection{Future work}
Although we  provide an  implementation for  a liveness  based garbage
collection scheme for lazy language, we  do not provide a formal proof
of its correctness.  A formal  proof of correctness would describe how
closures  are  handled  during  garbage  collection  and  liveness  is
propogated inside closures.
